Simple SIR

### 2018-05-22 SimpleSIR.Rmd
Update .Rmd formatting

#Load libraries
Load `deSolve` library for evaluating ordinary differntial equations (ODEs).
```{r setup}
library(deSolve)
library(ggplot2)
library(cowplot)
```

@@

##Run stochastic simulations
Run simplified SIR model for six combinations of conspecific density and recovery rate tested in spatially explicit model.

@@

##Plot deterministic and stochastic SIR results (assuming equal mixing)
Compare/verify output from deterministic ODE and stochastic SIR models
```{r}
setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/SimpleSIR")
#set wd to location of stochastic SIR simulation output files

@@

##Combine simulation ouput
```{r}
library(doBy)
library(ggplot2)
library(viridis)
library(ggthemes)
library(scales)
library(lsr)

@@

##Box plots
Box plots comparing density and recovery rates for homogenous mixing SIR model
```{r}
setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures Dec. 2017")
#sub_data<-merged_data[which(merged_data$max_I>1),] #successful outbreaks

@@

##Fig. S6
Compare homogenous mixing and spatial models in box plot form.
```{r}
setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/")
SIRdata_merged<-read.csv("SIRdata_merged.csv")
SIRdata_merged<-SIRdata_merged[,-1]

>>>>

## Load libraries
Load `deSolve` library for evaluating ordinary differntial equations (ODEs).
```{r setup}
library(deSolve)
library(ggplot2)
library(cowplot)
```

@@

## Run stochastic simulations
Run simplified SIR model for six combinations of conspecific density and recovery rate tested in spatially explicit model.

@@

## Plot deterministic and stochastic SIR results (assuming equal mixing)
Compare/verify output from deterministic ODE and stochastic SIR models
```{r}
setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/SimpleSIR")
#set wd to location of stochastic SIR simulation output files

@@

## Combine simulation ouput
```{r}
library(doBy)
library(ggplot2)
library(viridis)
library(ggthemes)
library(scales)
library(lsr)

@@

## Box plots
Box plots comparing density and recovery rates for homogenous mixing SIR model
```{r}
setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures Dec. 2017")
#sub_data<-merged_data[which(merged_data$max_I>1),] #successful outbreaks

@@

## Fig. S7
Compare homogenous mixing and spatial models in box plot form.
```{r}
setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/")
SIRdata_merged<-read.csv("SIRdata_merged.csv")
SIRdata_merged<-SIRdata_merged[,-1]
